---
title: "Geo_Data"
author: "Nils Tinner"
date: "`r Sys.Date()`"
output: html_document
---
This script implements the download and processing of geospatial data for model training. It builds upon the work of Moritz Burger but is more general.

First we download all data in a resolution of 5 meters. Please define the extent
```{r}
extent = c(xmin = 2594313, xmax = 2605813, ymin = 1194069, ymax = 1204804)
source("../R/download_geospatial.R")
download_geospatial(extent)

```

Then we process. Here we can define the resolution of each layer currently viable. Please feel free to add more layers and make a pull request.
```{r}
meters_burger <- tibble(
  Category = c("Land Cover Building", "Open Space Sealed", "Open Space Forest", "Open Space Garden", "Open Space Water", "Open Space Agriculture"),
  Variable = c("LC_B", "OS_SE", "OS_FO", "OS_GA", "OS_WA", "OS_AC"),
  Chosen_buffer_radiusm = c(250, 500, 250, 25, 150, 500)
)


# New entries to add
meters_new <- tibble(
  Category = c("Aspect", "Flow accumulation", "Roughness", "Slope", "Terrain index", "NDVI","DEM"),
  Variable = c("ASP", "FLAC", "ROU", "SLO", "TPI", "NDVI","DEM"),
  Chosen_buffer_radiusm = c(5, 125, 5, 5, 5, 250,5)
)
meters <- bind_rows(meters_burger, meters_new)

source("../R/processing_geospatial.R")
processing_geospatial(meters)
```

