---
title: "Geo_Data"
author: "Nils Tinner"
date: "`r Sys.Date()`"
output: html_document
---
This script implements the download and processing of geospatial data for model training. It builds upon the work of Moritz Burger but is more general.

First we download all data in a resolution of 5 meters. Please define the extent
```{r}
packages <- c('influxdbclient', 'ggplot2', 'tidyverse', 'lubridate', 'dplyr', 'caret',
              'vip', 'parsnip', 'workflows', 'tune', 'dials', 'stringr', 'terra', 'stars',
              'sf', 'plyr', 'doParallel', 'foreach', 'terrainr', 'starsExtra', 'pdp',
              'recipes', 'tidyterra', 'shiny', 'xgboost', 'kableExtra', 'rnaturalearth', 'zoo',
              'moments', 'tibble', 'rsample', 'yardstick', 'cowplot', 'purrr', 'renv',
              'ranger','Boruta','sp',"jsonlite","httr","scales","MODISTools")

# Load the R script to install and load all the packages from above
source("../R/load_packages.R")
load_packages(packages = packages)

# Define the extent: xmin = W, xmax = E, ymin = S, ymax = N, Coordinate system: CH1903+/LV95
city = "Thun"
#extent = c(xmin = 2594313, xmax = 2605813, ymin = 1194069, ymax = 1204804) # Bern
extent = c(xmin = 2608999, xmax = 2619222, ymin = 1173148, ymax = 1183507) # Thun
# city = "test"
# extent = c(xmin = 2594313, xmax = 2595000, ymin = 1194069, ymax = 1194600)
source("../R/download_geospatial.R")
download_geospatial(extent, city)
```

**Optional**: Calculate Altitude difference between DEM and location of MeteoCH reference station
```{r}
AD <- rast(paste0("../data-raw/", city, "/DEM.tif"))
AD <- AD - 570 # adapt to the location of the MeteoCH reference station
plot(AD)
writeRaster(AD, paste0("../data-raw/", city, "/AD.tif"), overwrite = TRUE)
```


Then we process. Here we can define the resolution of each layer currently viable. Please feel free to add more layers and make a pull request.
```{r}
meters_burger <- tibble(
  Category = c("Land Cover Building", "Open Space Sealed", "Open Space Forest", "Open Space Garden", "Open Space Water", "Open Space Agriculture"),
  Variable = c("LC_B", "OS_SE", "OS_FO", "OS_GA", "OS_WA", "OS_AC"),
  Chosen_buffer_radiusm = c(250, 500, 250, 25, 150, 500)
)


# New entries to add
meters_new <- tibble(
  Category = c("Aspect", "Flow accumulation", "Roughness", "Slope", "Terrain index", "NDVI","DEM"),
  Variable = c("ASP", "FLAC", "ROU", "SLO", "TPI", "NDVI","DEM"),
  Chosen_buffer_radiusm = c(5, 125, 5, 5, 5, 250,5)
)
meters <- bind_rows(meters_burger, meters_new)

source("../R/processing_geospatial.R")
processing_geospatial(meters)
```


Alternativly, one can also create several buffer zones by:

```{r}
meters_burger <- tibble(
  Category = c("Land Cover Building", "Open Space Sealed", "Open Space Forest", "Open Space Garden", "Open Space Water", "Open Space Agriculture", "Building Height", "Vegetation height"),
  Variable = c("LC_B", "OS_SE", "OS_FO", "OS_GA", "OS_WA", "OS_AC", "BH_NA", "VH"),
)

# Creating a new tibble for the buffer radius expansion
buffer_values <- tibble(Chosen_buffer_radiusm = c(25, 100, 175, 250, 500, 750, 1000))

# Expand meters_burger to include new Chosen_buffer_radiusm values by crossing with buffer_values
meters_burger <- crossing(meters_burger, buffer_values)

# New entries to add
meters_new <- tibble(
  Category = c("Aspect", "Flow accumulation", "Roughness", "Slope", "Terrain index","DEM", "Altitude Difference"),
  Variable = c("ASP", "FLAC", "ROU", "SLO", "TPI","DEM", "AD"),
)
buffer_values <- tibble(Chosen_buffer_radiusm = c(5, 50, 125, 250, 500))
meters_new <- crossing(meters_new, buffer_values)

meters <- bind_rows(meters_burger, meters_new)|>
  add_row(Category = "NDVI", Variable = "NDVI", Chosen_buffer_radiusm = c(250, 500)) # NDVI original resolution is 250

source("../R/processing_geospatial.R")
processing_geospatial(meters, city)
```

